MSTK: Mesh Toolkit, v 1.7

### 2011-02-18 docs/MSTK.tex
Updated documentation for version 1.8

\par MSTK will eventually support distributed meshes for parallel
computing. However, this is still not in place.

@@

MSTK offers a flexible infrastructure for representing and
manipulating meshes so that mesh-based application developers do not
have to deal with the complexitiies of managing their own data
structures. The functional interface of MSTK is designed to provide
easy access to mesh data and allow for easy-to-read but efficient code
to be written for mesh based applications. Accessing the mesh data
through the functional interface allows the high level application to
be unchanged even if the lower level data structures in MSTK
change. MSTK supports a wide array of element types and several
representations, all of which can take a new developer years to write
and make robust. New users of MSTK can typically start writing their
own codes to query and manipulate meshes within a few days of
familiarizing themselves with MSTK. Finally, use of MSTK allows easy
integration with other codes using MSTK as their mesh data framework.

@@

@@

There are a few ways of getting mesh data into MSTK. The first is to
prepare an MSTK file with the full connectivity of an F1
representation and to read it in using MESH\_InitFromFile. This is
typically a difficult task for many applications which only have
element-node data. In such cases, one can prepare an MSTK file in the
R1 file format (in which the node listing is followed by the
region-node connectivity) and read it in to any of the other
representations, say F1. The other possibility is to write a file in
the GMV format and use MESH\_ImportFromFile to import the mesh in.

MSTK can write meshes out to different formats including GMV, STL and
FLAG X3D. When compiled with the appropriate options and using a
partitioner from an external library, MSTK can also write out a
parallel X3D file.

@@

Unordered sets or lists of entities in MSTK are returned as type
{\em List\_ptr}. The following are the set operations available in
MSTK:

@@

\item[]{\bf {\em int} MESH\_ImportFromFile({\em Mesh\_ptr}
    mesh, const char *filename, const char *format):} Import a mesh
  data from an external file format and construct MSTK mesh. Currently
  the only format supported is the
  GMV\footnote{\texttt{http://www-xdiv.lanl.gov/XCM/gmv/GMVHome.html}}
  file format. The routine imports as many attributes as it can from
  the input file. It also uses special attributes or keywords as data
  about element and node classification.  For GMV files, the routine
  uses the ``material'' data to indicate region or face classification
  depending on the dimensionality of the mesh. If ``material'' data is
  not specified, it uses the ``itetclr'' attribute to assign region or
  face classification. It also uses the ``icr'' keyword describing the
  number of constraints on a node to interpret if the node is
  classified on a model region, model face, model edge or a model
  vertex. The ``itetclr'' and ``icr'' keywords are usually present in
  meshes generated by
  LAGRIT\footnote{\texttt{http://lagrit.lanl.gov}}.

@@

%% \item[]{\bf {\em void} MESH\_ExportToFile({\em Mesh\_ptr}
%%     mesh, const char *filname, const char *format, int natt, char
%%     **attnames):} Export a mesh to an external file format. Currently,
%%   the formats supported are the GMV file (format string: ``gmv'') and
%%   Data Explorer\footnote{\texttt{http://opendx.org}} (format string:
%%   ``dx''). Only integer and double attributes of the mesh are exported
%%   to the files.

\item[]{\bf {\em void} MESH\_ExportToFile({\em Mesh\_ptr} mesh, const
    char *filname, const char *format, int natt, char **attnames):}
  Export a mesh to an external file format. Currently, the only
  formats supported is the GMV file format (format string: ``gmv'')
  and X3D (format string: ``flag''). Only integer and double
  attributes of the mesh are exported to GMV files and no attributes
  are exported to X3D files.

\item[]{\bf {\em void} MESH\_ExportToGMV({\em Mesh\_ptr} mesh, const
    char *filname, const char *format, int natt, char **attnames):} Export a mesh to a GMV file format.

\item[]{\bf {\em void} MESH\_ExportToFLAGX3D({\em Mesh\_ptr} mesh, const
    char *filname, const char *format, int natt, char **attnames):} Export a mesh to the FLAG X3D format.

\item[]{\bf {\em void} MESH\_ExportToFLAGX3D\_Par({\em Mesh\_ptr} mesh,
    const char *filname, const char *format, int natt, char
    **attnames, int *procids):} Export a mesh to the FLAG X3D format
  given a partitioned mesh. The owning processor for each element is
  given in the array {\bf procids}.

\item[]{\bf {\em void} MESH\_ExportToSTL({\em Mesh\_ptr} mesh, const
    char *filname):} Export a mesh to the STL format (SURFACE MESHES ONLY!).

@@

@@

\item[]{\bf {\em MAttrib\_ptr}
    MESH\_AttribByName({\em Mesh\_ptr} mesh, {\em const char}
    *name):} Return a mesh attribute with given name if it exisists in
  the mesh. Returns NULL if mesh has no such attribute.

@@

\item[]{\bf {\em List\_ptr} MV\_Regions({\em MVertex\_ptr} mvertex):}
List of regions connected to the vertex. {\bf The list returned by this
  operator must be deleted by the calling application using {\em List\_Delete}}.
\end{description}

@@

@@

@@

@@

@@

\item[]{\bf {\em void} List\_Mark({\em List\_ptr} list, {\em int} mkr):} Mark a set of entities with given marker.

\item[]{\bf {\em void} List\_Unmark({\em List\_ptr} list, {\em int} mkr):}
Unmark a set of entities with respect to the given marker.

@@

>>>>

\par MSTK has preliminary support of distributed meshes for parallel
computing.

@@

MSTK offers a flexible infrastructure for representing and
manipulating meshes in a distributed environment so that mesh-based
application developers do not have to deal with the complexitiies of
managing their own data structures. The functional interface of MSTK
is designed to provide easy access to mesh data and allow for
easy-to-read but efficient code to be written for mesh based
applications. Accessing the mesh data through the functional interface
allows the high level application to be unchanged even if the lower
level data structures in MSTK change. MSTK supports a wide array of
element types and several representations, all of which can take a new
developer years to write and make robust. New users of MSTK can
typically start writing their own codes to query and manipulate meshes
within a few days of familiarizing themselves with MSTK. Finally, use
of MSTK allows easy integration with other codes using MSTK as their
mesh data framework.

@@

\subsection{Parallel Mesh Management}

MSTK now has preliminary support for representation of distributed
surface and volume meshes for supporting parallel
simulations. \textit{This is an alpha functionality and the API or
  behavior of some functions is subject to revision.}

Currently, the only way to distribute meshes on multiple processors is
to perform a serial read on processor 0 and then distribute it to
however many processors are necessary. Mesh attributes and mesh entity
sets are appropriately partitioned and distributed to the different
processors. Functionality to read a pre-partitioned mesh is planned
for the future.

MSTK currently supports one (or no) layer of overlapped or ghost
entities between processors. If a surface mesh requests a layer of
ghost faces, then all lower order entities (edges and vertices)
forming the ghost faces are also ghosted. Similarly, if a volume mesh
requests a layer of ghost regions, all lower order entities (faces,
edges and vertices) forming the ghost regions are reproduced. Entities
that are owned by a processor but duplicated on another processor are
called {\em Overlap} entities. Entities that are duplicates of overlap
entities are called {\em Ghost} entities. The master processor ID of a
ghost entity is the processor ID that its corresponding overlap entity
lives on.

MSTK supports automatic updating of scalars, vectors and tensors on
mesh entities of all dimensions. The application can update the
attribute values on its owned entities and call MSTK to update the
attribute values on ghosts on other processors.

\textit{MSTK does not yet support parallel modification of meshes}.

@@

There are a few ways of getting mesh data into MSTK. The first is to
prepare an MSTK file with the full connectivity of an F1
representation and to read it in using MESH\_InitFromFile. This is
typically a difficult task for many applications which only have
element-node data. In such cases, one can prepare an MSTK file in the
R1 file format (in which the node listing is followed by the
region-node connectivity) and read it in to any of the other
representations, say F1.

It is also possible to import meshes in other formats into MSTK. Some
formats that MSTK can read from are the GMV format and the ExodusII
format. Applications can use MESH\_ImportFromFile to import the mesh
into MSTK.

MSTK can write meshes out to different formats including GMV, STL and
ExodusII and FLAG X3D. When compiled with the appropriate options and
using a partitioner from an external library, MSTK can also write out
a parallel X3D file.

@@

Unordered lists of entities in MSTK are returned as type {\em
  List\_ptr} (See MSets for named entity sets). The following are the
list operations available in MSTK:

@@

\item[]{\bf {\em int} MESH\_ImportFromFile({\em Mesh\_ptr} mesh, const
    char *filename, const char *format):} Import a mesh data from an
  external file format and construct MSTK mesh. Currently the formats
  supported are the
  GMV\footnote{\texttt{http://www-xdiv.lanl.gov/XCM/gmv/GMVHome.html}}
  file format and the Exodus II file format. The routine imports as
  many attributes as it can from the input file. It also uses special
  attributes or keywords as data about element and node
  classification.  For GMV files, the routine uses the ``material''
  data to indicate region or face classification depending on the
  dimensionality of the mesh. If ``material'' data is not specified,
  it uses the ``itetclr'' attribute to assign region or face
  classification. It also uses the ``icr'' keyword describing the
  number of constraints on a node to interpret if the node is
  classified on a model region, model face, model edge or a model
  vertex. The ``itetclr'' and ``icr'' keywords are usually present in
  meshes generated by
  LAGRIT\footnote{\texttt{http://lagrit.lanl.gov}}. For Exodus II file
  formats, element blocks are used to create sets of mesh regions with
  the name 'matset\_N' (where N is the element block ID), sidesets are
  used to create sets of faces named 'sideset\_N' and nodesets are used
  to create sets of vertices named 'nodeset\_N'.

@@

  \item[]{\bf {\em void} MESH\_ExportToFile({\em Mesh\_ptr} mesh,
      const char *filname, const char *format, int natt, char
      **attnames):} Export a mesh to an external file
    format. Currently, the formats supported are the GMV file format
    (format: ``gmv'') and X3D (format: ``flag''), Exodus II file
    format (format: ``exodusii''). In addition surface meshes may be
    exported to STL (format: ``stl'') and IBM Data Explorer (format:
    ``dx'') format. Only integer and double attributes of the mesh are
    exported to GMV files and no attributes are exported to X3D files.

  \item[]{\bf {\em void} MESH\_ExportToGMV({\em Mesh\_ptr} mesh, const
      char *filname, int natt, char **attnames):} Export a mesh to a
    GMV file format.

\item[]{\bf {\em void} MESH\_ExportToFLAGX3D({\em Mesh\_ptr} mesh,
    const char *filname, int natt, char **attnames):} Export a mesh to
  the FLAG X3D format.

\item[]{\bf {\em void} MESH\_ExportToFLAGX3D\_Par({\em Mesh\_ptr}
    mesh, const char *filname, int natt, char **attnames, int
    *procids):} Export a mesh to the FLAG X3D format given a
  partitioned mesh. The owning processor for each element is given in
  the array {\bf procids}.

\item[]{\bf {\em void} MESH\_ExportToExodusII({\em Mesh\_ptr} mesh,
    const char *filname, int natt, char **attnames):} Export a mesh to
  a GMV file format.

\item[]{\bf {\em void} MESH\_ExportToDX({\em Mesh\_ptr} mesh, const
    char *filname):} Export a mesh to the IBM Data Explorer format
  (SURFACE MESHES ONLY!).

@@

\item[]{\bf {\em MEntity\_ptr} MESH\_EntityFromID({\em Mesh\_ptr}
    mesh, {\em MType mtype}, {\em int} id):} Return mesh entity of
  given type and given ID if it exists; return NULL otherwise.

@@

\item[]{\bf {\em MAttrib\_ptr}
    MESH\_AttribByName({\em Mesh\_ptr} mesh, {\em const char}
    *name):} Return a mesh attribute with given name if it exists in
  the mesh. Returns NULL if mesh has no such attribute.

\item[]{\bf {\em int} MESH\_Num\_MSets({\em Mesh\_ptr}
    mesh):} Number of entity sets associated with the mesh.

\item[]{\bf {\em MSet\_ptr} MESH\_MSet({\em Mesh\_ptr}
    mesh, {\em int} i):} Return the i'th entity set in the mesh.
  Returns NULL if i $<$ 0 or i $>$ number of entity sets.

\item[]{\bf {\em MSet\_ptr}
    MESH\_Next\_MSet({\em Mesh\_ptr} mesh, {\em int} *index):}
  Returns the next entity set while iterating through the sets of
  the mesh. See the routine List\_Next\_Entry above for an explanation
  of how the iteration works.

\item[]{\bf {\em MSet\_ptr}
    MESH\_MSetByName({\em Mesh\_ptr} mesh, {\em const char}
    *name):} Return a mesh entity set with given name if it exists in
  the mesh. Returns NULL if mesh has no such set.

@@

\item[]{\bf {\em List\_ptr} MV\_Regions({\em MVertex\_ptr} mvertex):}
List of regions connected to the vertex. {\bf The list returned by this
  operator must be deleted by the calling application using {\em List\_Delete}}.

\item[]  {\bf {\em PType} MV\_PType({\em MVertex\_ptr} v)}: Parallel entity type for vertex - can be PINTERIOR, POVERLAP or PGHOST.
\item[]  {\bf {\em int}   MV\_MasterParID({\em MVertex\_ptr} v)}:
\item[]  {\bf {\em int}   MV\_GlobalID({\em MVertex\_ptr} v)}:

\item[]
\item[]  The following three functions affect how mesh entities communicate and how their attributes are updated. IF YOU DON'T KNOW WHAT YOU ARE DOING WHEN YOU CALL THIS FUNCTION, YOU WILL GET WHAT YOU DESERVE.
\item[]  {\bf {\em void}  MV\_Set\_PType({\em MVertex\_ptr} v, {\em PType} ptype)}: 
\item[]  {\bf {\em void}  MV\_Set\_MasterParID({\em MVertex\_ptr} v, {\em int} masterparid)}
\item[]  {\bf {\em void}  MV\_Set\_GlobalID({\em MVertex\_ptr} v, {\em int} globalid)}:

@@

\item[]  {\bf {\em PType} ME\_PType({\em MEdge\_ptr} v)}: Parallel entity type for edge - can be PINTERIOR, POVERLAP or PGHOST.
\item[]  {\bf {\em int}   ME\_MasterParID({\em MEdge\_ptr} v)}:
\item[]  {\bf {\em int}   ME\_GlobalID({\em MEdge\_ptr} v)}:

\item[]
\item[]  The following three functions affect how mesh entities communicate and how their attributes are updated. IF YOU DON'T KNOW WHAT YOU ARE DOING WHEN YOU CALL THIS FUNCTION, YOU WILL GET WHAT YOU DESERVE.
\item[]  {\bf {\em void}  ME\_Set\_PType({\em MEdge\_ptr} v, {\em PType} ptype)}: 
\item[]  {\bf {\em void}  ME\_Set\_MasterParID({\em MEdge\_ptr} v, {\em int} masterparid)}
\item[]  {\bf {\em void}  ME\_Set\_GlobalID({\em MEdge\_ptr} v, {\em int} globalid)}:

@@

\item[]  {\bf {\em PType} MF\_PType({\em MFace\_ptr} v)}: Parallel entity type for face - can be PINTERIOR, POVERLAP or PGHOST.
\item[]  {\bf {\em int}   MF\_MasterParID({\em MFace\_ptr} v)}:
\item[]  {\bf {\em int}   MF\_GlobalID({\em MFace\_ptr} v)}:

\item[]
\item[]  The following three functions affect how mesh entities communicate and how their attributes are updated. IF YOU DON'T KNOW WHAT YOU ARE DOING WHEN YOU CALL THIS FUNCTION, YOU WILL GET WHAT YOU DESERVE.
\item[]  {\bf {\em void}  MF\_Set\_PType({\em MFace\_ptr} v, {\em PType} ptype)}: 
\item[]  {\bf {\em void}  MF\_Set\_MasterParID({\em MFace\_ptr} v, {\em int} masterparid)}
\item[]  {\bf {\em void}  MF\_Set\_GlobalID({\em MFace\_ptr} v, {\em int} globalid)}:

@@

\item[]  {\bf {\em PType} MR\_PType({\em MRegion\_ptr} v)}: Parallel entity type for edge - can be PINTERIOR, POVERLAP or PGHOST.
\item[]  {\bf {\em int}   MR\_MasterParID({\em MRegion\_ptr} v)}:
\item[]  {\bf {\em int}   MR\_GlobalID({\em MRegion\_ptr} v)}:

\item[]
\item[]  The following three functions affect how mesh entities communicate and how their attributes are updated. IF YOU DON'T KNOW WHAT YOU ARE DOING WHEN YOU CALL THIS FUNCTION, YOU WILL GET WHAT YOU DESERVE.
\item[]  {\bf {\em void}  MR\_Set\_PType({\em MRegion\_ptr} v, {\em PType} ptype)}: 
\item[]  {\bf {\em void}  MR\_Set\_MasterParID({\em MRegion\_ptr} v, {\em int} masterparid)}
\item[]  {\bf {\em void}  MR\_Set\_GlobalID({\em MRegion\_ptr} v, {\em int} globalid)}:

@@

\newpage
\subsection{Mesh Sets}

Mesh sets are unordered but named sets of entities. MSets can be
queried and modified just like Lists. However, unlike Lists, MSets are
associated with a mesh, can be constrained to contain only particular
types of entities and have boolean operations performed on them.

\item[]{\bf {\em MSet\_ptr} MSet\_New({\em Mesh\_ptr} mesh, {\em const
      char} *set\_name, {\em MType} entdim):} Define a new mesh entity
  set. Along with the mesh to which this set is assigned ({\bf mesh})
  and the name of the set ({\bf att\_name}), the the dimension of the
  entities that the set can contain must be specified as {\bf
    MVERTEX}, {\bf MEDGE}, {\bf MFACE}, {\bf MREGION} or {\bf
    MALLTYPE}.

\item[]{\bf {\em char} *MSet\_Name({\em MSet\_ptr} set, {\em char}
    *att\_name):} Get the name of the given set.

\item[]{\bf {\em MType} MSet\_EntDim({\em MSet\_ptr} set):} Get the
  dimension of entities the set can contain. Can be {\bf MVERTEX},
  {\bf MEDGE}, {\bf MFACE}, {\bf MREGION} or {\bf MALLTYPE}.

\item[]{\bf {\em Mesh\_ptr} MSet\_Mesh({\em MSet\_ptr} set):}
Returns the mesh that the entity set belongs to.

\item[]{\bf {\em void} MSet\_Delete({\em MSet\_ptr} set):} Delete an
  set.

\item[]{\bf {\em MSet\_ptr} MSet\_Add({\em MSet\_ptr} l, {\em void
      *}entry):} Add an entry to the set. The entry is strictly
  appended to the end of the set.

\item[]{\bf {\em MSet\_ptr} MSet\_ChknAdd({\em MSet\_ptr} l, {\em void
      *}entry):} Add an entry to a set only if it is not already in
  the set.

\item[]{\bf {\em MSet\_ptr} MSet\_Insert({\em MSet\_ptr} l, {\em void
      *}nuentry, {\em void *}b4entry):} Insert an entry into the set
  in the position before 'b4entry'.

\item[]{\bf {\em MSet\_ptr} MSet\_Inserti({\em MSet\_ptr} l, {\em void
      *}nuentry, {\em int} i):} Insert an entry into the set at the
  i'th valid position and push the entries previously at the i'th and
  later position back.

\item[]{\bf {\em int} MSet\_Rem({\em MSet\_ptr} l, {\em void
      *}entry):} Remove an entry from the set. Returns 1 if
  successful, 0 otherwise.

\item[]{\bf {\em int} MSet\_Remi({\em MSet\_ptr} l, {\em int} i):}
  Remove the i'th valid entry in the set. Returns 1 if successful, 0
  otherwise.

\item[]{\bf {\em int} MSet\_Replace({\em MSet\_ptr} l, {\em void
      *}entry, {\em void *}nuentry):} Replace 'entry' with 'nuentry'
  in set. Returns 1 if successful, 0 otherwise.

\item[]{\bf {\em int} MSet\_Replacei({\em MSet\_ptr} l, {\em int} i,
    void *nuentry):} Replace the i'th valid entry in the set with
  'nuentry'. Returns 1 if successful, 0 otherwise.

\item[]{\bf {\em int} MSet\_Contains({\em MSet\_ptr} l, void *entry):}
  Returns 1 if set contains the entry, 0 otherwise.

\item[]{\bf {\em int} MSet\_Locate({\em MSet\_ptr} l, void *entry):}
  Returns the positional index of the entry in the set. Returns -1 if
  the set does not contain the entry.

\item[]{\bf {\em void *}MSet\_Entry({\em MSet\_ptr} l, {\em int} i):}
  Return the i'th valid entry in the set.  Returns a NULL pointer if
  the i'th valid entry could not be found.

\item[]{\bf {\em void *}MSet\_Next\_Entry({\em MSet\_ptr} l, {\em int}
    *i):} Return the next valid entry in the set. This routine works
  just like List\_Next\_Entry.

\item[]{\bf {\em int} MSet\_Num\_Entries({\em MSet\_ptr} l):} Return
  the number of entries in a set.

\item[]{\bf {\em MSet\_ptr} MSets\_Union({\em MSet\_ptr} s1, {\em
      MSet\_ptr} s2):} Create a new set from the union of two sets.

\item[]{\bf {\em MSet\_ptr} MSets\_Intersect({\em MSet\_ptr} s1, {\em
      MSet\_ptr} s2):} Create a new set from the intersection of two
  sets. Routine returns null if the intersection is a null set.

\item[]{\bf {\em MSet\_ptr} MSets\_Subtract({\em MSet\_ptr} s1, {\em
      MSet\_ptr} s2):} Create a new set by subtracting set 2 from set
  1. Routine returns null if the result is a null set.

@@

\item[]{\bf {\em void} List\_Mark({\em List\_ptr} list, {\em int} mkr):} Mark a list of entities with given marker.

\item[]{\bf {\em void} List\_Unmark({\em List\_ptr} list, {\em int} mkr):}
Unmark a list of entities with respect to the given marker.

\item[]{\bf {\em void} MSet\_Mark({\em MSet\_ptr} list, {\em int} mkr):} Mark a set of entities with given marker.

\item[]{\bf {\em void} MSet\_Unmark({\em MSet\_ptr} list, {\em int} mkr):}
Unmark a set of entities with respect to the given marker.

@@

\newpage 
\subsection{Parallel Mesh Management}

The following are the highest level of parallel mesh management functions.

\item[] {\bf {\em int} MSTK\_Mesh\_Read\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em const char*} global\_mesh\_name, {\em int} dim,
    {\em int} ring, {\em int} with\_attr, {\em int} rank, {\em int}
    num, {\em MPI\_Comm} comm)}: Routine reads a mesh of dimension
  'dim' from file 'global\_mesh\_name' on processor 'rank' and
  distributes it 'num' processors. 'comm' is the communicator to be
  used by MPI. If 'ring' is 0, there is no overlap of the highest
  level entities between processors - only entities on processor
  boundaries will be duplicated on other processors. If 'ring' is N,
  then 'N' layers of the highest level entities will overlap between
  processors ({\em Currently, only 1 layer of overlap elements are
    supported}). If 'with\_attr' is 1, then MSTK sets up the links
  necessary to synchronize attribute data across processors. This routine must be called from only one processor.

\item[] {\bf {\em int} MSTK\_Mesh\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em int} ring, {\em int} with\_attr, {\em int}
    rank, {\em int} num, {\em MPI\_Comm} comm)}: Similar to the above
  Read\_Distribute routine except that it does do any read. On the
  processor, that is doing the distributing, recv\_mesh holds the
  input and out meshes.

\item[] {\bf {\em int} MSTK\_UpdateAttr({\em Mesh\_ptr} mesh, {\em
      int} rank, {\em int} num, {\em MPI\_Comm} comm)}: Update the
  attributes of duplicated entities on remote processors.

For users requiring more fine grain control of their application, the
following a list of lower level parallel mesh functions. Descriptions
of these functions will be added soon. {\bf NOTE THAT THESE ROUTINES
  HAVE NOT IN ANYWAY BEEN MADE IDIOT-PROOF AND REQUIRE GOOD KNOWLEDGE
  OF THE PARALLEL MODEL IN MSTK.}

  \item[] {\bf {\em int} MSTK\_SendMesh({\em Mesh\_ptr} mesh, {\em int} rank, {\em int} with\_attr, {\em MPI\_Comm} comm)}:

  \item[] {\bf {\em int} MSTK\_RecvMesh({\em Mesh\_ptr} mesh, {\em int} dim, {\em int} send\_rank, {\em int} rank, {\em int} with\_attr, {\em MPI\_Comm} comm)}:

  \item[] {\bf {\em int} MESH\_PartitionWithMetis({\em Mesh\_ptr} mesh, {\em int} nparts, {\em int} **part)}:
  \item[] {\bf {\em int}        MSTK\_Mesh\_Partition({\em Mesh\_ptr} mesh, {\em Mesh\_ptr} *submeshes, {\em int} num, 				 {\em int} ring, {\em int} with\_attr)}
  \item[] {\bf {\em int}        MESH\_Partition({\em Mesh\_ptr} mesh, {\em Mesh\_ptr} *submeshes, {\em int} num)}
  \item[] {\bf {\em int}        MESH\_CopyAttr({\em Mesh\_ptr} mesh, {\em Mesh\_ptr} submesh, {\em const char} *attr\_name)}

  \item[] {\bf {\em int}        MESH\_BuildPBoundary({\em Mesh\_ptr} mesh, {\em Mesh\_ptr} submesh)}

  \item[] {\bf {\em int}        MESH\_AddGhost({\em Mesh\_ptr} mesh, {\em Mesh\_ptr} submesh, {\em int} part\_no, {\em int} ring)}

  \item[] {\bf {\em int}        MESH\_SendMesh({\em Mesh\_ptr} mesh, {\em int} rank, {\em MPI\_Comm} comm)}
  \item[] {\bf {\em int}        MESH\_SendAttr({\em Mesh\_ptr} mesh, {\em const char} *attr\_name, {\em int} rank, {\em MPI\_Comm} comm)}
  \item[] {\bf {\em int}        MESH\_RecvMesh({\em Mesh\_ptr} mesh, {\em int} dim, {\em int} send\_rank, {\em int} rank, {\em MPI\_Comm} comm)}
  \item[] {\bf {\em int}        MESH\_RecvAttr({\em Mesh\_ptr} mesh, {\em const char} *attr\_name, {\em int} rank, {\em int} recv\_rank, {\em MPI\_Comm} comm)}

  \item[]{\bf {\em int} MESH\_Num\_GhostVertices({\em Mesh\_ptr} mesh):}
    Number of ghost vertices in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_GhostEdges({\em Mesh\_ptr} mesh):}
    Number of ghost edges in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_GhostFaces({\em Mesh\_ptr} mesh):}
    Number of ghost faces in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_GhostRegions({\em Mesh\_ptr} mesh):}
    Number of ghost regions in the mesh.

  \item[]{\bf {\em MVertex\_ptr} MESH\_GhostVertex({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th ghost vertex in the mesh. Returns NULL if i
    $<$ 0 or i $>$ number of mesh vertices.

  \item[]{\bf {\em MEdge\_ptr} MESH\_GhostEdge({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th ghost edge in the mesh. Returns NULL if i $<$
    0 or i $>$ number of mesh edges. Returns NULL for reduced
    representations.

  \item[]{\bf {\em MFace\_ptr} MESH\_GhostFace({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th face in the mesh. Returns NULL if i $<$
    0 or i $>$ number of mesh faces. Only faces explicitly represented in
    the mesh are returned for reduced representation.

  \item[]{\bf {\em MRegion\_ptr} MESH\_GhostRegion({\em Mesh\_ptr} mesh, {\em
        int} i):} Return the i'th region in the mesh. Returns NULL if i
    $<$ 0 or i $>$ number of mesh region.

  \item[]{\bf {\em MVertex\_ptr} MESH\_Next\_GhostVertex({\em Mesh\_ptr}
      mesh, {\em int} *idx):} Returns the next ghost vertex while iterating
    through the vertices of the mesh. See the routine {\bf
      List\_Next\_Entry} above for an explanation of how the iteration
    works. This routine is in general faster than using the routine {\bf
      MESH\_GhostVertex}.

  \item[]{\bf {\em MEdge\_ptr} MESH\_Next\_GhostEdge({\em Mesh\_ptr} mesh,
      {\em int} *idx):} Returns the next ghost edge while iterating through the
    edges of the mesh. See the routine List\_Next\_Entry above for an
    explanation of how the iteration works.  The routine always returns
    NULL for reduced representations.

  \item[]{\bf {\em MFace\_ptr} MESH\_Next\_GhostFace({\em Mesh\_ptr} mesh,
      {\em int} *idx):} Returns the next ghost face while iterating through the
    faces of the mesh. See the routine {\bf List\_Next\_Entry} above for
    an explanation of how the iteration works.  Only faces explicitly
    represented in the mesh are returned for reduced representation.

  \item[]{\bf {\em MRegion\_ptr}
      MESH\_Next\_GhostRegion({\em Mesh\_ptr} mesh, {\em int} *idx):}
    Returns the next region while iterating through the regions of the
    mesh. See the routine {\bf List\_Next\_Entry} above for an
    explanation of how the iteration works.

  \item[]{\bf {\em int} MESH\_Num\_OverlapVertices({\em Mesh\_ptr} mesh):}
    Number of overlap vertices in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_OverlapEdges({\em Mesh\_ptr} mesh):}
    Number of overlap edges in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_OverlapFaces({\em Mesh\_ptr} mesh):}
    Number of overlap faces in the mesh.

  \item[]{\bf {\em int} MESH\_Num\_OverlapRegions({\em Mesh\_ptr} mesh):}
    Number of overlap regions in the mesh.

  \item[]{\bf {\em MVertex\_ptr} MESH\_OverlapVertex({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th overlap vertex in the mesh. Returns NULL if i
    $<$ 0 or i $>$ number of mesh vertices.

  \item[]{\bf {\em MEdge\_ptr} MESH\_OverlapEdge({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th overlap edge in the mesh. Returns NULL if i $<$
    0 or i $>$ number of mesh edges. Returns NULL for reduced
    representations.

  \item[]{\bf {\em MFace\_ptr} MESH\_OverlapFace({\em Mesh\_ptr} mesh,
      {\em int} i):} Return the i'th face in the mesh. Returns NULL if i $<$
    0 or i $>$ number of mesh faces. Only faces explicitly represented in
    the mesh are returned for reduced representation.

  \item[]{\bf {\em MRegion\_ptr} MESH\_OverlapRegion({\em Mesh\_ptr} mesh, {\em
        int} i):} Return the i'th region in the mesh. Returns NULL if i
    $<$ 0 or i $>$ number of mesh region.

  \item[]{\bf {\em MVertex\_ptr} MESH\_Next\_OverlapVertex({\em Mesh\_ptr}
      mesh, {\em int} *idx):} Returns the next overlap vertex while iterating
    through the vertices of the mesh. See the routine {\bf
      List\_Next\_Entry} above for an explanation of how the iteration
    works. This routine is in general faster than using the routine {\bf
      MESH\_OverlapVertex}.

  \item[]{\bf {\em MEdge\_ptr} MESH\_Next\_OverlapEdge({\em Mesh\_ptr} mesh,
      {\em int} *idx):} Returns the next overlap edge while iterating through the
    edges of the mesh. See the routine List\_Next\_Entry above for an
    explanation of how the iteration works.  The routine always returns
    NULL for reduced representations.

  \item[]{\bf {\em MFace\_ptr} MESH\_Next\_OverlapFace({\em Mesh\_ptr} mesh,
      {\em int} *idx):} Returns the next overlap face while iterating through the
    faces of the mesh. See the routine {\bf List\_Next\_Entry} above for
    an explanation of how the iteration works.  Only faces explicitly
    represented in the mesh are returned for reduced representation.

  \item[]{\bf {\em MRegion\_ptr}
      MESH\_Next\_OverlapRegion({\em Mesh\_ptr} mesh, {\em int} *idx):}
    Returns the next region while iterating through the regions of the
    mesh. See the routine {\bf List\_Next\_Entry} above for an
    explanation of how the iteration works.
